\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-13 ext-ind-type-compilation-example.tex
Fix Module tm_var_handle.

\begin{lstlisting}
(* Type checking of Recursion *) [@\tanc{Tyck-RecTy-start}@]
(* Typecheck each handler, here STLC.subst.tm_var *)
(* Also an example of fields in nested family [@\dadada@]*) 
Module tm_var_handle (STLC: STLC_Ctx1)[@\YZ{(1) Why doesn't the module name contain "subst"? (2) Should it be STLC_Ctx2 instead of STLC_Ctx1?}\EDJreply{I rename to ctx so that I think it is easier to understand. Feel Free to change to the way you want. I think name them all into "_Ctx" suffix is easier to emphasize the fact they are the result of compilation of the context. (2) The fact is, no, it also will need to include tm_prec's computational axiom and ty, which I also forgot to mention. Also ty has its prec and computational axiom. So at least 6. Do you want me to write doesn STLC_Ctx(1,2,3,4,5,6)? It is unnecessary complication and the space is not enough. I proposed to move this part of information into the figure 5 toy example in the slack, what do you think? }@]
    (self: EmptySig). (* [@\dadada@] thus with two contexts *)[@\YZ{(3) Are nested families really needed?}\EDJreply{Not really but if consider handlers as one family, it is nested family. What's more, the audience needs to know how nested family is compiled at some point.}@]
  Definition tm_var s x t := 
    if eqb x s then t else STLC.tm_var s.
End tm_var_handle. (* [@\dadada@] other handlers are alike *)
(* Assembling tycked handlers in STLC.subst *)
Module subst_internal_410 (M: STLC_Ctx1). 
 Module subst_internal.
 Include tm_var_handle M. Include tm_abs_handle M.
 Include tm_app_handle M. Include tm_unit_handle M.
 End subst_internal.
End subst_internal_410.
(* Intermediate Module solely for exhausitivity checking *) 
Module do_tc (self: STLC_Ctx[@\dadada@]).
  Include tm_rec_type self. 
  Include subst_internal_410 self.
  Parameter (for_tyck : _TYPE_tm_rec).
  Definition term_for_type_checking :=
    for_tyck  ( λ _  ⇒ (id → self.tm → self.tm))
      subst_internal.tm_var [@\dadada@] .
End do_tc.[@\tanc{Tyck-RecTy-end}@]
\end{lstlisting}

>>>>

\begin{lstlisting}
(* Type checking of Recursion *) [@\tanc{Tyck-RecTy-start}@]
(* Typecheck each handler, here STLC.subst.tm_var *)
(* Also an example of fields in nested family [@\dadada@]*) 
Module tm_var_handle (STLC: STLC_Ctx1).[@\YZ{(1) Why doesn't the module name contain "subst"? (2) Should it be STLC_Ctx2 instead of STLC_Ctx1?}\EDJreply{I rename to ctx so that I think it is easier to understand. Feel Free to change to the way you want. I think name them all into "_Ctx" suffix is easier to emphasize the fact they are the result of compilation of the context. (2) The fact is, no, it also will need to include tm_prec's computational axiom and ty, which I also forgot to mention. Also ty has its prec and computational axiom. So at least 6. Do you want me to write doesn STLC_Ctx(1,2,3,4,5,6)? It is unnecessary complication and the space is not enough. I proposed to move this part of information into the figure 5 toy example in the slack, what do you think? }@]
[@\YZ{(3) Are nested families really needed?}\EDJreply{Not really but if consider handlers as one family, it is nested family. What's more, the audience needs to know how nested family is compiled at some point.}@]
  Definition tm_var s x t := 
    if eqb x s then t else STLC.tm_var s.
End tm_var_handle. (* [@\dadada@] other handlers are alike *)
(* Assembling tycked handlers in STLC.subst *)
Module subst_internal_410 (M: STLC_Ctx1). 
 Module subst_internal.
 Include tm_var_handle M. Include tm_abs_handle M.
 Include tm_app_handle M. Include tm_unit_handle M.
 End subst_internal.
End subst_internal_410.
(* Intermediate Module solely for exhausitivity checking *) 
Module do_tc (self: STLC_Ctx[@\dadada@]).
  Include tm_rec_type self. 
  Include subst_internal_410 self.
  Parameter (for_tyck : _TYPE_tm_rec).
  Definition term_for_type_checking :=
    for_tyck  ( λ _  ⇒ (id → self.tm → self.tm))
      subst_internal.tm_var [@\dadada@] .
End do_tc.[@\tanc{Tyck-RecTy-end}@]
\end{lstlisting}
